### 2017-02-15 real/draft.tex
[draft] Clarify motivation for large n

\subsection{Single-packet description}

@@

>>>>

\subsection{Single-packet description} \label{sec:single-packet}

@@

In practice, the situation may arise that many packets fall into a
bin. One can then avoid modeling the luminosity distribution
explicitly as done in \refsec{single-packet} as it becomes irrelevant
in the limit $n \to \infty$, essentially due to the central limit
theorem. As a bonus, the numerical effort to evaluate the basic
\refeq{sll} drastically simplifies.
